Lucky Thirteen - A Cryptographic Analyses

### 2013-07-10 paper.tex
First few point identified

\section{Introduction}
\label{Introduction}

>>>>

\section{Introduction}
\label{sec:intro}

\section{Short overview of Cryptography in TLS}
\label{sec:crypto}

\section{Padding Oracle Attacks}

\label{sec:paddingoracle}
\subsection{}

\subsection{Bomb Oracles}
\label{sec:paddingoracle:bomb}
blabla $\oplus$ blabla

\section{TLS}
\label{sec:TLS}
TLS 1.1 and 1.2: check the padding format carefully, report a single error message for padding and MAC failures, and make the record processing time essentially the same whether or not the padding is correct.

\section{Lucky Thirteen}
\label{sec:lucky}
regular plaintext recovery of a block: 2\^23 connections
if base64 (cookies, http basic access authentication) used: 2\^23 -> 2\^19 connection per block
per cookie byte, using BEAST technique: 2\^13 connections

\section{The Future of TLS}
\label{sec:future}
